BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-04-04 tex/answers-to-reviewers-comments.txt

> ----------------------- REVIEW 1 ---------------------
> page 2, footnote 1:
> The term "insufficient amount of text" needs a couple of lines more
> explanation. Why does this lead to a failure?
We added two sentences to clarify this, but I would also like to give a
concrete example. On this blog post [1], the textual content of the post is "A
floral embroidered coat seems to be all the rage on chic girls this Winter".
Now suppose that the layout adds some noise, for instance by also containing
in deepest div containing with the article the text "facebook twitter email 27
comments Posted in Women Tags: Coats, If You're Thinking About....". Then the
div containing the title of the post, "If You’re Thinking About... Floral
Embroidered Coats", or even the div of one of the comment, might be the more
similar to the text provided than the actual article div.

[1]: <http://www.thesartorialist.com/photos/if-youre-thinking-about-floral-embroidered-coats/>

> section 2.4, 2nd paragraph:
> A definition of n is missing (although it can be guessed).
We added it.

> section 2.5, 7th paragraph:
> This paragraph is hard to follow! What is "an overflow on its comment feed"?
> Do you mean comments content arriving by means of AJAX calls? Please
> explain. The second sentence of the paragraph is also not clear ("..narrow
> down ...fixint a target..."). Please rewrite this paragraph.
Indeed this paragraph was not very clear. The information it contained was
also really not important so we decided to remove it all together. The first
sentence was a repetition of the "Similarly to blog feeds..." sentence in the
paragraph before the bullet points: if the comment feed is not full there is
no need to extract comments from the page. Regarding the "comment content is
extracted first", this is a small optimization I did to first get the exact
number of comments by matching the comment content (which is usually more
unique and accurate that doing a matching on author/date), and use this number
to then accurately get the other fields.

> section 3.1, 3rd paragraph: Is the modularity mentioned available in the
> current system implementation? For example, can you "sense" somehow the
> presence of JavaScript content so as to exclude the "Render JavaScript" step
> in the pipeline?
Not this modularity is only "at source code level", but the pipeline is not
dynamically modified at runtime. We added some clarifications on this.

> section 3.2, 2nd paragraph:
> who is building the regular expressions out of the blog post URLs? Is it
> done manually or automatically? Please clarify. Additionally, what if the
> blog does not use friendly URLs (which they do support well the idea of
> constructing regular expressions out of the URLs)? Consider for example a
> WordPress based blog with URLs of the form http://<domain>/?p=234. How such
> a non informative URL affects your approach?
We included precisions on this (automatic) process. For a blog with URLs on
the format of "http://example.com/?p=234", the generated regular expression
will be something like ^http://example.com/?[a-zA-Z0-9]+=[0-9]+$.

> section 3.2, 4th paragraph:
> The priority queue used, prioritizes the URLs based on a machine learning
> algorithm trained on the basis of the URL and the number of links it
> contains.
> a) Is there any assumption here that the links of the page lead to plog
>    posts? Why do URLs with more links are preferred?
> b) What is the aim here? To prioritize or to prune? The former makes no
>    sense (at the end you will have to deal with all the pages). The latter,
>    if it holds, is not clear - I was expecting to read about some threshold
>    value under which pages are dropped out of the queue.
> Please clarify both the above.
a) The "blog post identification function" described before serves this
   purpose.
b) The aim is to prune uninteresting pages, we wrote an additional paragraph
   to make this clear. It explains that this mechanism allows to add
   "termination conditions" in order to save some resources. Studying this
   kind or engineering coefficient/heuristic requires to experiment with a
   large amount of blogs, which was out of the scope of this paper.

> ----------------------- REVIEW 2 ---------------------
> The only comment is that the authors could have used some of the non-used
> space (8 out of 12 pages) to further discuss some of the pointed directions
> for future work.
We extensively discussed this point at the beginning of our work on the
crawler, and we decided to split the work into two parts. We originally aimed
for the "short paper" format, and planned our work to have it ready for the
first deadline (09/12/13), but we did not evaluated the length properly and
finally switched to the "full paper" format.

### 2014-04-05 tex/runningtimeFigure.tex
Invert legend order on the grnuplot figure
Formatting revisions

    set title 'Figure \arabic{figure}: Running time of articles extraction.'
    set ylabel 'Cumulated running time (sec.)' offset 1.3
    set xlabel 'Processed blog posts'

    set yrange [0:44]
    set xrange [0:65]

>>>>

    set title '\textbf{Figure \arabic{figure}: Running time of article extraction}'
    set ylabel 'Cumulated running time (sec.)' offset 1.3
    set xlabel 'Processed blog posts'

    set yrange [0:44]
    set xrange [0:65]
    set key invert
